Shortest path algorithms are of central importance in Computer Science. 
A particularly fascinating aspect of these algorithms is 
that they can often be generalized to rather exotic algebraic structures
such as \emph{semirings}~\cite{gondran_graphs_2008}.  
A semiring $(S,\ \oplus,\ \otimes,\ \overline{0},\ \overline{1})$ is 
comprised of a commutative monoid $(S,\ \oplus,\ \overline{0})$ 
and a monoid $(S,\ \otimes,\ \overline{1})$ such that 
two \emph{distributivity axioms} hold: 
for all $a, b, c \in S$, 
\begin{equation}
\label{eq:left:distributivity}
    a\otimes (b \oplus c) = (a\otimes b) \oplus (a\otimes c), 
\end{equation}
\begin{equation}
\label{eq:right:distributivity}
    (b \oplus c) \otimes a = (b\otimes a) \oplus (c\otimes a). 
\end{equation}
A directed graph having $n$ nodes and arc weights in $S$ 
can be represented as a $n\times n$-matrix $\mathbf{A}$ over $S$. 
Given a path $p = v_0, v_1, \cdots,\ v_k$ (a sequence of nodes), 
its {\em weight} is defined as 
\begin{equation}
\label{eq:def:weight}
    w_{\mathbf{A}}(p) 
    \equiv 
    \mathbf{A}(v_0,\ v_1) 
    \otimes \mathbf{A}(v_0,\ v_1) 
    \otimes \cdots 
    \otimes \mathbf{A}(v_{k-1},\ v_k),  
\end{equation}
with the empty path given the weight $\overline{1}$. 

The generalized shortest-path problem is then to find 
a matrix $\mathbf{A}^*$ such that 
\begin{equation}
\label{eq:global}
\mathbf{A}^*(i,\ j) = \displaystyle\bigoplus_{p \in \pi(i,\ j)} w_{\mathbf{A}}(p) 
\end{equation}
where $\pi(i,\ j)$ represents the set of all paths from node $i$ to node $j$. 
Such solutions do not always exist, and SAY SOMETHING 


For the reader not familiar with this generalization 
we define the \emph{shortest paths semiring} as 
\begin{equation}
\label{eq:def:sp}
\mathbb{sp} \equiv (\mathbb{N},\ \min,\ +, \infty,\ 0),
\end{equation}
where path weight is just the sum of arc weights
To get some feeling for the power of the 
algebraic approach consider the semiring 
\begin{equation}
\label{eq:def:cap}
\mathbb{cap} \equiv (\mathbb{N},\ \max,\ \min,\ 0,\ \infty),
\end{equation}
which can be used to compute \emph{maximum capacity paths}. 
The weight of a path is determined by $\min$ to be the 
weight of a bottleneck arc.  
The key here is that a generic implementation of a shortest
paths algorithm can be developed and then instantiated with 
different semirings. 

The interested reader can find a thorough treatment of 
this material in~\cite{gondran_graphs_2008}.   

\subsection{Dropping distributivity} 

It is well known that if $\mathbf{A}^*$ exists, then it 
is a solution of the (left) equation 
\begin{equation}
\label{eq:left:local}
\mathbf{L} = (\mathbf{A}\otimes \mathbf{L}) \oplus \mathbf{I}
\end{equation}
as well as the (right) equation 
\begin{equation}
\label{eq:right:local}
\mathbf{R} = (\mathbf{R}\otimes \mathbf{A}) \oplus \mathbf{I}. 
\end{equation}

The distributivity axioms, 
Equations~\ref{eq:left:distributivity} and~\ref{eq:left:distributivity}, 
are essential in the semiring theory outlined above. 
Thus it may seem suprising that recent research has shown that
the matrix equations ~\ref{eq:left:local} and ~\ref{eq:right:local} 
can sometimes be solved even if when 
distributivity axioms do not hold in the algebraic structure employed. 
Much of this work was originally motivated 
by investigations of the Border Gageway Protocol (BGP), 
the Internet routing protocol which has evolved to 
maintains global connectivity between Internet Service Providers (ISPs). 
In BGP the anologue of the weight of a path 
$p = v_0, v_1, \cdots,\ v_k$ at node $v_0$ 
is dominated by the contractural relationships between 
the networks associated with nodes $v_0$ and $v_1$.
The typical relationships involve those between customers 
and providers and between competing ISPs (that must exchange
routing information in order to provide connectivty to 
the global Internet).  

But how can we interpret such solutions? 
Take Equation~\ref{eq:left:local} for example. 
If we assume that $\mathbf{L}$ solves this equation 
and that $i \neq j$, then we have 
\begin{equation}
\label{eq:left:local:at:i}
\mathbf{L}(i,\ j) = \displaystyle\bigoplus_{q \in N(i)} \mathbf{A}(i,\ q) \otimes \mathbf{L}(q,\ j), 
\end{equation}
where $N(i)$ is the set of neighbors of node $i$. 
We can interpret this from node $i$'s perspective as 
the best path weight available given the paths its neighbors 
have obtained. 
That is, $\mathbf{L}$ does not represent the globally optimal 
path weights, but rather an equilibrium point that we will 
call \emph{locally optimal}. 


%\paragraph{Contributions and map of paper}
%\subsection{Map of Paper}
%\label{subsect.map.of.paper}
%In Section~\ref{sect.basic.definitions} we cover some definitions needed to define Dijkstra's algorithm and its correctness proof.
%In Section~\ref{sect.path.algebras.their.properties.and.models} we discuss `path algebras', a variety of algebraic structure central to our proof of correctness, also providing three models of path algebras to demonstrate that models exist and that path algebras are not categorical.
%In Section~\ref{sect.dijkstras.algorithm.and.its.correctness} we discuss the imperative Dijkstra algorithm, our functional implementation, and main body of the correctness proof leading up to our main theorem: Dijkstra's algorithm computes a right-local solution.
%In Section~\ref{sect.example} we demonstrate the algorithm in action with an example execution inside Agda.
%In Section~\ref{sect.conclusions} we conclude.

